Network and Routing

### 2023-06-15 data-raw/01-OSM-Network-and-Routing.Rmd
Tracking noebooks and cache files

---
title: "Network-Preprocessing"
author: "Antonio Paez"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

Load packages:
```{r}
# Allocate memory
options(java.parameters = "-Xmx20G")

@@

  # export output as disk.frame
  ifelse(i == 1, output_df <- as.disk.frame(ttm_chunk,
                                            nchunks = 1,
                                            outdir = "./df/output_ttm_walk",
                                            compress = 50,
                                            overwrite = TRUE),
         add_chunk(output_df, ttm_chunk, chunk_id = i))
  setTxtProgressBar(pb, i)
}
end.time <- Sys.time()
ttm_walk_time <- end.time - start.time
ttm_walk_time
```

>>>>

---
title: "Network and Routing"
author: "Antonio Paez"
date: "`r Sys.Date()`"
output: html_notebook
---

@@

Load packages:
```{r}
# Allocate memory for routing
options(java.parameters = "-Xmx20G")

@@

  # export output as disk.frame
  ifelse(i == 1, output_df <- as.disk.frame(ttm_chunk,
                                            nchunks = 1,
                                            outdir = "./df/output_ttm_walk",
                                            compress = 50,
                                            overwrite = TRUE),
         add_chunk(output_df, ttm_chunk, chunk_id = i))
  setTxtProgressBar(pb, i)
}

end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken
```
